Through the eyes of the teacher

### 2021-02-24 paper_1/paper_1_supplement_new_table.Rmd
scale analysis + correlation presence items

# correlation between all presences' items
cor.test(self.p.wide$phb_alleangesehen, self.p.wide$phb_alleangesehen, method=c("pearson"))

@@

stud.alpha.p <- alpha(stud.p.wide[,-1])
stud.alpha.p

>>>>

##############################################
# #####correlation between all presences' items
# SELF-ASSESSMENT
# install.packages("Hmisc")
library("Hmisc")

# function to format the correlation matrix
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}

res1.self<-rcorr(as.matrix(self.p.wide[,-1]))

flattenCorrMatrix(res2$r, res2$P)

res2.self<-flattenCorrMatrix(res2$r, res2$P)

# Visualization correlation matrix
# Use corrplot() function: Draw a correlogram

# install.packages("corrplot")
library("corrplot")

# Insignificant correlation are crossed
corrplot(res1.self$r, type="upper", order="hclust",
         p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
# Insignificant correlations are leaved blank
corrplot(res1.self$r, type="upper", order="hclust",
         p.mat = res1.self$P, sig.level = 0.01, insig = "blank")

@@

stud.alpha.p <- alpha(stud.p.wide[,-1])
stud.alpha.p
##############################################
# #####correlation between all presences' items
# SELF-ASSESSMENT
# install.packages("Hmisc")
library("Hmisc")

# function to format the correlation matrix
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}

res1.stud<-rcorr(as.matrix(stud.p.wide[,-1]))

flattenCorrMatrix(res1.stud$r, res1.stud$P)

res2.stud<-flattenCorrMatrix(res1.stud$r, res1.stud$P)

# Visualization correlation matrix
# Use corrplot() function: Draw a correlogram

# install.packages("corrplot")
library("corrplot")

# Insignificant correlation are crossed
corrplot(res1.stud$r, type="upper", order="hclust",
         p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
# Insignificant correlations are leaved blank
corrplot(res1.stud$r, type="upper", order="hclust",
         p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
###############################################
